% {{{ Document preamble - JIRA Rules

\documentclass[10pt]{beamer}%

\title{I\&D Atlassian JIRA Rules}%
\date{\today}%
\author{Gary A. Howard}%

\usetheme{Havasu}

% -------------------------------------------------------------------------- }}}
% {{{ Begin Presentation

\begin{document}%

% -------------------------------------------------------------------------- }}}
% {{{ Title page

\begin{frame}%
\titlepage%
\begin{center}%
  \textcolor{HavasuBlue}{v1.1}%
\end{center}%
\end{frame}%

% -------------------------------------------------------------------------- }}}
% {{{ JIRA Assignee

\begin{frame}%
  \frametitle{\hspace{4mm}JIRA issue}%
  \framesubtitle{\hspace{4mm}All issues must have an Assignee}%
  %
  \begin{mdframed}[style=HavasuLightBlueStyle]%
    \textbf{Rule \#1}\\%
    The law of non-contradiction states that contradictory propositions cannot
    be both true in the same sense at the same time.  Therefore, we can conclude
    if an issue is ``In progress'' is \textbf{must} have an ``Assignee''.
  \end{mdframed}%
  %
  \begin{mdframed}[style=HavasuLightGreenStyle]%
    \textbf{Assignee is applied to:}%
    \begin{itemize}%
      \item Epics%
      \item Stories%
      \item Tasks%
      \item Subtask%
      \item Bugs%
    \end{itemize}%
  \end{mdframed}%
  %
\end{frame}%

% -------------------------------------------------------------------------- }}}
% {{{ Story point values using a Fibonacci sequence.

\begin{frame}%
  \frametitle{\hspace{4mm}JIRA Issue Estimations}%
  \framesubtitle{\hspace{4mm}All assignments must use the same story point values.}%
  %
  \begin{mdframed}[style=HavasuLightBlueStyle]%
    \textbf{Rule \#2}\\%
    \textbf{All} JIRA issue shall use the following Fibonacci sequence when
    estimating, and be decomposed to one of these values.
  \end{mdframed}%
  %
  \begin{mdframed}[style=HavasuLightGreenStyle]%
    \textbf{Story point values:}%
    \begin{itemize}%
      \item  $1.0 \Rightarrow  0.0 \leq\  2.5 hrs$%
      \item  $2.0 \Rightarrow  2.5 \leq\  5.0 hrs$%
      \item  $3.0 \Rightarrow  5.0 \leq\  8.0 hrs$%
      \item  $5.0 \Rightarrow  8.0 \leq\ 16.0 hrs$%
      \item  $8.0 \Rightarrow 16.0 \leq\ 24.0 hrs$%
      \item $13.0 \Rightarrow 24.0 \leq\ 32.0 hrs$%
    \end{itemize}%
  \end{mdframed}%
  %
\end{frame}%

% -------------------------------------------------------------------------- }}}
% {{{ Team responsibilities

\begin{frame}%
  \frametitle{\hspace{4mm}Daily Responsibilities}%
  \framesubtitle{\hspace{4mm}All assignments must use the same story point values.}%

  \begin{mdframed}[style=HavasuLightBlueStyle]%
    \textbf{Rule \#3}\\%
    \textbf{All} JIRA issues shall be managed daily.
  \end{mdframed}%
  %
  \begin{mdframed}[style=HavasuLightGreenStyle]%
    \textbf{Daily expectations:}%
    \begin{itemize}%
      \item Assign the JIRA issue to yourself the moment you begin work.
      \item Team members shall hold each other accountable for team data.
      \item Scrum masters shall monitor this and report repeat offenders.
    \end{itemize}%
  \end{mdframed}%
  %
\end{frame}%

% -------------------------------------------------------------------------- }}}
% {{{ End Presentation

\end{document}%

% -------------------------------------------------------------------------- }}}
